When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added license to plots

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}

@@

```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

@@

```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level. Each dot indicates a participant, the colours indicate their Need for Cognition (NFC) score. $N=116$. There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity.", fig.pos="H"}

@@

```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (left) and aversiveness ratings (right) when subtracting 2- from 1-back and 3- from 2-back. Each line indicates a participant, the colours indicate their Need for Cognition (NFC) score. $N=116$.", fig.pos="H"}

@@

```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$.", fig.pos="H"}

>>>>

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

@@

```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

@@

```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level. Each dot indicates a participant, the colours indicate their Need for Cognition (NFC) score. $N=116$. There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

@@

```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (left) and aversiveness ratings (right) when subtracting 2- from 1-back and 3- from 2-back. Each line indicates a participant, the colours indicate their Need for Cognition (NFC) score. $N=116$. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

@@

```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
